\section{Related Work}
\label{sec:related_work}

\subsection{Optimizing Secure Storage on Accelerators}
\label{sec:related_sim}

There have been many studies that optimize secure storage and cryptographic execution to enhance performance on high-end hardware. Previous studies~\cite{flashneuron, fscrypt_gpu, fastensor} focused on utilizing massive parallelism in GPUs and distributed clusters for high-throughput cryptographic operations. These approaches accelerate execution and extend scalability by distributing the block files across aggregated memory in leadership-class datacenter systems. Other studies~\cite{fastensor, fscrypt_gpu} have proposed static compilation and batch scheduling techniques to reduce transfer overhead. These methods analyze storage block jobs in advance to generate optimized execution plans or precompiled kernels, aiming to maximize kernel occupancy and minimize inter-device data transfer. In addition, hardware-based approaches have been proposed~\cite{optee, dmcrypt} to reduce the CPU footprint by offloading cryptographic logic. These methods provide significant CPU savings for large-scale databases but face severe latency-overhead growth when running concurrent edge applications with high resource contention.

Our study aligns with these prior efforts in improving the computational efficiency of secure storage. However, AEGIS-Q aims to democratize secure storage by targeting resource-constrained edge devices rather than relying on dedicated datacenter accelerators. Existing datacenter-centric approaches such as fscrypt-GPU~\cite{fscrypt_gpu} assume abundant memory resources and high-bandwidth interconnects, which leads to execution failures on embedded devices where physical memory is strictly limited. AEGIS-Q addresses this limitation by trading execution speed for QoS preservation. It partitions the block jobs across the CPU/GPU memory hierarchy and employs a specialized execution pipeline, enabling large-scale post-quantum secure storage on commodity hardware without requiring dedicated accelerator partitions.

\subsection{Memory Extension and QoS-Aware Storage}
\label{sec:related_mem}

To address the memory scalability bottleneck, several studies have explored alternative memory hierarchies and data representations. Previous studies~\cite{snuqs_storage, infscaler} extended storage capacity by offloading block staging to high-performance SSDs. These approaches manage the movement of data pages between host memory and storage to support executions exceeding physical DRAM capacity. Other studies~\cite{breaking_edge, flashneuron} have proposed lossless compression and adaptive error-bounded encoding techniques to reduce memory consumption. These methods dynamically compress block buffers during storage operations, allowing systems to store larger datasets within limited memory footprints. In the context of edge computing, research has primarily focused on trusted execution environments (TEEs) and lightweight post-quantum cryptography (PQC) rather than full QoS-aware storage architectures. While standard trusted execution environments~\cite{optee} support secure storage operations on CPU, they lack specific optimizations for the memory hierarchy of edge devices.

Our study aligns with these prior efforts in utilizing storage offloading and memory virtualization. However, AEGIS-Q differs by targeting the unique Unified Memory Architecture (UMA) of edge devices. Previous storage-based cache managers such as SnuQS~\cite{snuqs_storage} rely on CPU-centric memory paging which incurs high synchronization overhead, while other frameworks compete for limited GPU resources on embedded systems. Through a UVM-aware asynchronous pipeline, AEGIS-Q integrates storage offloading and PQC execution into a unified framework that minimizes CPU-GPU synchronization. Additionally, it exploits the zero-copy capabilities of edge architectures to overlap data movement with computation. This allows AEGIS-Q to achieve a 128$\times$ capacity expansion and support secure operations on low-power devices, surpassing the capabilities of prior storage-extended frameworks.
