\section{Conclusion}
\label{sec:conclusion}

We presented AEGIS-Q, the first GPU-accelerated secure storage runtime optimized for resource-constrained IoT edge devices. By integrating a tiered execution and memory hierarchy (GPU VRAM $\to$ CPU DRAM $\to$ NVMe SSD) with adaptive admission control, AEGIS-Q enables secure storage scales previously limited to dedicated hardware cryptosystems.

\paragraph{Key Results}
\begin{itemize}
  \item \textbf{High-Throughput Cryptographic Staging}: 1 TB raw data block processing on an 8 GB Jetson Orin Nano (\$200, 15W) --- a 128$\times$ capacity expansion through zero-copy tiered staging.
  \item \textbf{Multi-Workload Benchmarks}: Across ML-KEM, SHA-256 leaf hashing, and TPM anchoring, demonstrating consistent scaling across diverse secure storage structures.
  \item \textbf{100\% AI QoS Preservation}: On TensorRT YOLOv8 inference under heavy concurrent I/O pressure, fully restoring the tail latency (0.91\,ms) and frame rate.
\end{itemize}

\paragraph{Honest Performance Comparison} Datacenter cryptosystems achieve massive throughput using hundreds of GPUs. In contrast, AEGIS-Q requires 3.3 hours for a 1 TB block sequential PQC key rotation and staging. This performance difference is expected --- our contribution is demonstrating that high-security post-quantum secure storage can be integrated into resource-constrained edge systems without violating foreground real-time AI QoS.

\paragraph{Limitations} (1) Execution time scales super-linearly due to scheduling overhead; (2) Admission efficiency degrades when the inference workload is highly dynamic; (3) Single-device execution limits throughput.

\paragraph{Future Work} Multi-device Jetson clusters for distributed secure storage; hardware-aware PQC compilation; hybrid edge-cloud secure database execution.

\paragraph{Availability} AEGIS-Q is open-source at \url{https://github.com/sunggonkim/IoTJ-AEGIS-Q}.
