\section{Implementation}
\label{sec:design_impl}

AEGIS-Q is implemented in C/CUDA on FUSE3.  The source tree splits the FUSE adapter, fd-context lifecycle, writeback/publication, epoch log, recovery, anchor, keyring/KDF, QoS, POSIX policy, and CUDA executors across \texttt{code/}; \texttt{pqc\_fuse.c} is mount-facing.  The build enables \texttt{-Wall -Wextra -Werror} for C/C++ and builds CUDA targets only when cuPQC is present.

Table~\ref{tab:impl_boundaries} summarizes choices that are easy to misread.  Publication is a strict data/journal/checkpoint path plus opt-in epoch-redo-log grouping, not an accelerator path.  GPU AES-GCM is format-compatible and falls back to CPU, but evaluated data writes are CPU-first.  The GPU ML-KEM executor is not an in-place filesystem data path; integrity parity tests do not imply a persisted per-file Merkle tree or side-channel protection.

\begin{table}[t]
\centering
\caption{Implementation boundaries that are easy to misread without an explicit summary.}
\begin{tabularx}{\columnwidth}{P{0.28\columnwidth}|Y|Y}
\toprule
\textbf{Mechanism} & \textbf{Current implementation} & \textbf{Boundary}\\
\midrule
CUDA storage path & Managed allocation with explicit prefetch and stream synchronization & Not an NVMe-to-UVM storage-DMA path\\
CUDA failure policy & CUDA executor falls back to CPU on failure & Does not change the on-disk record format\\
Anchor backend & File witness plus optional hardware NV index backend & Hardware path requires administrator pre-provisioning\\
Scheduler fallback & No-slack jobs route to CPU & No optimistic GPU admission without producer-supplied slack\\
\bottomrule
\end{tabularx}
\label{tab:impl_boundaries}
\end{table}

The key-envelope path generates a random DEK, wraps it under the mount key, HMAC-authenticates the envelope, and rejects failed authentication before ciphertext is read.  ML-KEM is optional batched maintenance: ordinary mounts with no rekey trigger allocate no ML-KEM object, KEM keypair, background rekey worker, CUDA AES executor, elastic admission state, scheduler accounting, QoS monitor, external anchor, or managed GPU buffer.  Forced or interval rekey can refresh open-file DEK material and persist new HMAC envelopes, but the format does not pretend that a KEM benchmark is a persistent per-file key hierarchy.  The worker collects up to 128 envelopes with a 1~ms default window, skips admission setup until the candidate batch reaches the GPU byte gate, and suppresses successful per-batch logs unless diagnostic verbosity is requested.

The older \texttt{pqc\_file\_key.*} epoch/grace helper remains source-only and is not linked into \texttt{pqc\_fuse}; evaluated epochs are open-file refresh bookkeeping, not stale-handle, rollback, or TPM/PCR-bound rollback proof.

The implementation also fails closed in two places.  A scheduler job with no producer-supplied slack is routed to CPU.  A requested TPM backend with no pre-provisioned NV index causes initialization to fail rather than creating a persistent index with undocumented ownership.  These are conservative operational choices; neither substitutes for a complete external foreground-workload telemetry integration or TPM policy design.

\subsection{Persistent-object layout}

Each protected file is represented by ordinary lower-filesystem state rather than an in-kernel extent map.  The data sidecar stores encrypted records; the metadata sidecar stores logical-block to record mappings and authentication material; xattrs store compact metadata such as logical size and the authenticated envelope.  This layout is intentionally inspectable for fault-injection experiments: a harness can copy or corrupt a backing directory, restore an older sidecar, or mutate an xattr without requiring a custom block device.

The layout also creates concrete assumptions.  AEGIS-Q relies on the lower filesystem to honor completed \texttt{fdatasync} order for data then metadata sidecars and to preserve checkpoint xattrs according to documented semantics.  The remount oracle accepts a mapping only when referenced ciphertext, journal record, and authenticated checkpoint/xattr state are visible together.  Reordering after acknowledged sync or lost xattrs is outside the selected crash model.  This separates the invariant---data is synced before mapping publication---from certifying every lower-filesystem, directory, rename, drive-cache, or physical power-loss interleaving.

\subsection{Concurrency and unsupported modes}

The evaluated path uses ordinary FUSE read, write, flush, fsync, open, and release operations.  The implementation keeps the CPU data path separate from the elastic lane in three concrete ways.

First, foreground AES-GCM flushes bypass scheduler target construction.  They do not construct write-admission contexts, read GPU telemetry, or execute a GPU admit/release branch.  Runtime byte accounting follows the actual flush extent, so CPU-published AES-GCM records are not reported as GPU work and partial overwrites do not inflate GPU queue pressure by file size.

Second, disabled diagnostics are not on the common path.  FUSE latency tracing, durability timing, write-throttle thresholds, telemetry polling, rekey write-trigger policy, trace sinks, parallel-commit trace snapshots, fault cutpoints, publication knobs, grouping knobs, and external-anchor backend selection are cached, initialized at mount time, or guarded by fast gates.  Default mounts therefore avoid repeated environment parsing, trace open/close, per-operation timestamp collection, and disabled diagnostic atomics.  The GPU-load polling thread is also lazy: it does not start unless QoS throttling, a telemetry file, an explicit GPU-load path, or an explicit monitor request is configured.

Third, repeated local work was removed from the mounted read/write path.  The common path avoids same-daemon metadata reloads, sidecar EOF probes, empty-flush/release drain checks, read/write scratch allocation churn, per-open success logging, post-open policy-context relocking, redundant flush-descriptor clearing, redundant full-batch reinitialization, redundant read-side zeroing, and whole-buffer sidecar-path clearing.  FUSE read/write scratch is ordinary CPU memory; CUDA managed allocation and prefetch are confined to executor-owned buffers and explicit diagnostics.

Strict publication drains coalesced writes before sync returns, updates sidecar dirty epochs and D/J append cutpoints at batch boundaries, and records per-block ciphertext offsets before journal mapping preparation.  Without an external anchor backend, checkpoint xattr verification skips committed-prefix map construction, anchor-worker staging, and fsync-time anchor flush; same-size strict overwrites reuse the reserved final checkpoint instead of rewriting identical xattr bytes.  Epoch mode can group selected barriers while replaying only committed prefixes.  These choices are performance engineering inside the scoped runtime contract, not a general high-throughput filesystem claim.

The implementation is not presented as a full POSIX conformance layer.  In particular, the paper does not claim validated shared \texttt{mmap} semantics, all possible concurrent-writer races, cross-process byte-range lock compatibility, or arbitrary rename/directory-fsync crash behavior.  Those modes are common sources of filesystem bugs, and the review correctly identified them as missing evidence.  Treating them as unsupported or unvalidated is preferable to silently inheriting a POSIX claim from FUSE.

\subsection{Telemetry plumbing}

The admission logic is implemented as ordinary C state rather than a separate daemon that invents scheduling results.  It records input queue depth, batch size, slack, telemetry age, and route decision.  On the elastic path, cumulative route counters and telemetry samples are read through atomic snapshots, and trace emission first checks a cached trace-enabled gate before taking the trace lock.  The mounted-FUSE throttle path reads a telemetry file and applies hysteresis before sleeping inside the write-flush path.  The tegrastats and CUPTI harnesses differ only in how they populate that telemetry input.  This shared path is the reason the evaluation can claim same-run telemetry-to-FUSE wiring; it is still a storage-runtime result rather than an external application scheduler.
