\PassOptionsToPackage{expansion=false}{microtype}
\documentclass[sigconf,nonacm,screen]{acmart}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{braket}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{pifont,array}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{nccmath}
\usepackage{xurl}
\usepackage{xspace}
\usepackage{comment}
\usepackage{makecell, kotex}
\usepackage{colortbl}
\usepackage[most]{tcolorbox}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% Tables contain capability boundaries.  Ragged columns avoid
% both misleading word spacing and overfull boxes in the two-column format.
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}

\captionsetup{font=small}
\setlength{\textfloatsep}{6pt plus 1.0pt minus 1.0pt}
\setlength{\floatsep}{5pt plus 1pt minus 1pt}
\setlength{\intextsep}{5pt plus 1pt minus 1pt}
\setlength{\emergencystretch}{1.5em}
\raggedbottom
\DeclareUnicodeCharacter{2713}{\checkmark}


\definecolor{pred}{rgb}{0.7843, 0.0039, 0.3137}
\definecolor{dblue}{rgb}{0.0, 0.0, 1.0}
\definecolor{sorange}{rgb}{0.91, 0.45, 0.32}
\newcommand{\skim}[1]{{\color{sorange}{#1}}} %
\newcommand{\changjong}[1]{{\color{pred}{#1}}}
    

\usetikzlibrary{fit,shapes,arrows,positioning}

%% Commands
\newcommand{\edgeQsim}{\texttt{AEGIS-Q}\xspace}
\newcommand{\EdgeQuantum}{\texttt{AEGIS-Q}\xspace}



\newcommand{\cmark}{{\color{green!70!black}\ding{51}}}
\newcommand{\xmark}{{\color{red!80!black}\ding{55}}}
\newcommand{\pmark}{{\color{orange!80!black}$\triangle$}}

\title{AEGIS-Q: A UMA-Aware Secure Edge File-Encryption Runtime}
\author{Changjong Kim}
\email{changjong5238@seoultech.ac.kr}
\affiliation{\institution{Seoul National University of Science and Technology}\city{Seoul}\country{Republic of Korea}}
\author{Ehan Sohn}
\email{ehanjsohn@seoultech.ac.kr}
\affiliation{\institution{Seoul National University of Science and Technology}\city{Seoul}\country{Republic of Korea}}
\author{Yongseok Son}
\email{sysganda@cau.ac.kr}
\affiliation{\institution{Chung-Ang University}\city{Seoul}\country{Republic of Korea}}
\author{Sunggon Kim}
\email{sunggonkim@seoultech.ac.kr}
\affiliation{\institution{Seoul National University of Science and Technology}\city{Seoul}\country{Republic of Korea}}

\renewcommand\shortauthors{Kim et al.}
\setcopyright{none}
\acmConference[SOSP 2026]{ACM Symposium on Operating Systems Principles}{2026}{}
\acmBooktitle{Proceedings of the ACM Symposium on Operating Systems Principles, 2026}
\acmISBN{}
\acmDOI{}
\acmYear{2026}
\acmSubmissionID{}
\acmPrice{}
\citestyle{acmnumeric}
\setlength{\bibsep}{-0.8pt}
\renewcommand{\bibfont}{\fontsize{4.85}{5.15}\selectfont}
\settopmatter{printacmref=false, printccs=false, printfolios=true}

\begin{document}
\begin{abstract}
Unified-memory edge devices co-locate local databases, encrypted logs, cache-manifest updates, and encrypted state on shared DRAM/storage.  A secure file-encryption runtime must place cryptographic work, not merely accelerate it: GPU work can steal bandwidth from foreground storage and durable publication.  Its thesis is that secure edge storage should expose \mbox{one durable authenticated format} with a CPU-first AES-GCM data plane and an elastic GPU/PQC maintenance lane.  AEGIS-Q explores that boundary as a boundary-aware UMA FUSE runtime with optional batched PQC key-plane maintenance, executor-local managed-memory use, and fail-closed external-anchor replay-after-advance checks.
The core result is asymmetric placement under edge pressure.  AES-GCM file records remain CPU-first; ML-KEM/cuPQC work uses the GPU only when it is independent, batched, and slack-tolerant; storage-visible QoS throttles elastic writes rather than weakening publication order.  On a Jetson AGX Thor Developer Kit, unthrottled secure-storage pressure reports 9.62~ms SQLite p99 and 6.98~MB/s background writes; AEGIS-Q reports 8.15~ms p99, zero median misses, and 3.02~MB/s background writes, while app-only is 7.25~ms.  The same mounted path exercises remount/tamper checks, generation faults, rekey fallback, selected app-crash timing, and telemetry-to-FUSE throttling.  This is a scoped edge file-encryption runtime result, not deployed-filesystem or peak-throughput superiority.
\end{abstract}

\keywords{Post-Quantum Cryptography, Edge Computing, Secure Storage, Unified Memory, TPM, FUSE}

\maketitle

\input{1_Introduction.tex}
\input{2_Background.tex}
\input{3_Design.tex}
\input{7_Implementation_Details.tex}
\input{8_Security_Analysis.tex}
\input{4_Evaluation.tex}
\input{10_Discussion_and_Limitations.tex}
\input{5_Related_Works.tex}
\input{6_Conclusion.tex}
% ACM bibliography style for conference-format builds
\newcommand{\aegisqsuppressurl}[1]{\unskip}
\let\showURL\aegisqsuppressurl
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
